Distinguishing NFW and Isothermal Density Profiles with Weak Gravitational Lensing

### 2018-05-05 paper.tex
building up methods section. nothing much just barebones for now
More elaboration in the abstract, as well as the beginning of the intro

\begin{abstract}
We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
\end{abstract}

\section{Introduction}
Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.

\subsection{General spherical density profile $\rho(r)$}
Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.

Projected surface density at radius R
\[\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}\]

Average projected surface density within radius R
\[\overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}\]

Critical surface density
\[\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}\]

@@

\section{Methods}

>>>>

\begin{abstract}
We examine the feasibility of distinguishing NFW and cored isothermal density profiles using weak gravitational lensing shear.
 To do so, we use Python to model lenses in the two different profiles, as well as background galaxies to be lensed.
 Analyzing the data of these lensed galaxies gives us insight into how we can distinguish the differences between the two profiles.
\end{abstract}

\section{Introduction}
Two commonly used density profiles in weak gravitational lensing are the isothermal profile and the Navarro-Frenk-White (NFW) profile.
We start with introducing the general characteristics of spherical density profiles, followed by cored isothermal and NFW profiles.
We then describe the purpose of our project, to distinguish between NFW and isothermal profiles, in detail.

\subsection{General spherical density profile $\rho(r)$}
We describe the common characteristics of spherical density profiles.
Here we define our conventions for various lensing quantities, which mainly conform to those used by \citet{Dodelson2017}. We use the thin lens approximation and assume spherical lens profiles.

The projected surface density at radius R is defined by
\[\Sigma(R) = \int_{-\infty}^{\infty}{dz\ \rho(\sqrt{R^2 + z^2})}\]

while the average projected surface density within R is
\[\overline{\Sigma}(R) = \frac{1}{\pi R^2} \int_0^{2\pi}{d\phi \int_0^{R}{dR'~\Sigma(R')R'}}\]

The critical surface density is
\[\Sigma_\mathrm{crit} = \frac{c^2}{4\pi G} \frac{D_S}{D_{SL} D_L}\]

@@

\section{Methods}
\subsection{Calculation of Shear and Deflection Angles for Each Profile}

\subsection{Modelling of Foreground Lens and Background Galaxies}
